Enhancing Forecast Reconciliation: A Study of Alternative Covariance Estimators

### 2025-10-21 thesis/paper_draft.qmd
organise old functions and re render

sim1_1 <- readRDS(paste0(path_lib, "S4-2-1_T50_M500.rds"))
sim1_2 <- readRDS(paste0(path_lib, "S4-2-1_T300_M500.rds"))

@@

sim_dense_50 <- readRDS(paste0(path_lib, "S100-10-3-1_T50_M200_dense.rds"))
sim_dense_300 <- readRDS(paste0(path_lib, "S100-10-3-1_T300_M200_dense.rds"))

sim_sparse_50 <- readRDS(paste0(path_lib, "S100-10-3-1_T50_M500_sparsebwgrp.rds"))
sim_sparse_300 <- readRDS(paste0(path_lib, "S100-10-3-1_T300_M200_sparsebwgrp.rds"))

sim3_1 <- sim_dense_50 # using same with next section simulation
sim3_2 <- sim_dense_300

@@

```{r generate plots for A and Sigma}
MSE1_1 <- transform_sim_MSE(sim1_1$MSE, F) |> 
  filter(.model != "ols")
MSE1_2 <- transform_sim_MSE(sim1_2$MSE, F) |> 
  filter(.model != "ols")

MSE2_1 <- transform_sim_MSE(sim2_1$MSE, F) |> 
  filter(! .model %in% c("mint_n_hstep", "ols"))
MSE2_2 <- transform_sim_MSE(sim2_2$MSE, F) |> 
  filter(! .model %in% c("mint_n_hstep", "ols"))

MSE3_1 <- transform_sim_MSE(sim3_1$MSE, F)
MSE3_2 <- transform_sim_MSE(sim3_2$MSE, F) |> 
  filter(.model != "ols")

p1_A <- plot_heatmap(sim1_1$A, T) + 
  ggtitle("2x2 VAR(1) Coefficients Matrix")

p1_Sigma <- plot_heatmap(cov2cor(sim1_1$Sigma), T) + 
  ggtitle("2x2 Correlation Matrix of Innovation process")

@@

p3_Sigma <- plot_heatmap(cov2cor(sim3_1$Sigma), T) +
  ggtitle("Correlation Matrix of Innovation process")
```

@@

@@

sim_sparse_50 <- readRDS(paste0(path, "/thesis/lib/params_S100_10_3_1_sparse46.rds"))
sim_sparse_50$Sigma |>
  cov2cor() |> 
  plot_heatmap(T)
```

>>>>

@@

sim3_1 <- readRDS(paste0(path_lib, "S100-10-3-1_T50_M200_dense.rds"))
sim3_2 <- readRDS(paste0(path_lib, "S100-10-3-1_T300_M200_dense.rds"))

@@

@@

@@

p3_Sigma <- plot_heatmap(cov2cor(sim3_1$Sigma), T) +
  ggtitle("Correlation Matrix of Innovation process")

@@

sim_params_sparse <- readRDS(paste0(path, "/thesis/lib/params_S100_10_3_1_sparse46.rds"))
sim_params_sparse$Sigma |>
  cov2cor() |> 
  plot_heatmap(T)
```
